HTW Test Analysis

### 2023-08-18 Analysis/test_analysis-all.qmd

```{r}
pacman::p_load(tidyverse,data.table,lme4,emmeans,here)
d <- readRDS(here("data/dPrune-05-21-23.rds"))

@@

dtestAgg <- dtest %>% group_by(id,condit,catOrder,fb,vb,band,lowBound,highBound,input) %>% mutate(vxCapped=ifelse(vx>1600,1600,vx)) %>%
  summarise(vxMean=mean(vx),devMean=mean(dist),vxMed=median(vx),devMed=median(dist),
            vxMeanCap=mean(vxCapped),.groups = "keep")

```{r}
model <- lmer(devMean ~ condit * catOrder * fb + (1|id), data = dtestAgg)
summary(model)

```
Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * catOrder * fb + (1 | id)
   Data: dtestAgg

@@

Fixed effects:
                                   Estimate Std. Error t value
(Intercept)                         212.430     13.967  15.209
conditVaried                         53.614     19.965   2.685
catOrderrev                           9.478     21.811   0.435
fbordinal                            56.609     22.441   2.523
conditVaried:catOrderrev            -45.098     30.951  -1.457
conditVaried:fbordinal              -58.510     33.172  -1.764
catOrderrev:fbordinal               -12.767     32.312  -0.395
conditVaried:catOrderrev:fbordinal   -3.604     47.473  -0.076

@@

- The intercept (212.430) represents the estimated mean devMean for the reference group (constant training, 'orig' order, and continuous feedback).
- conditVaried (53.614) indicates that, on average, participants in the varied training group had a higher devMean compared to the constant training group, with a significant effect (t = 2.685).
- catOrderrev (9.478) suggests that the 'rev' order manipulation had a small and non-significant effect on devMean (t = 0.435).
- fbordinal (56.609) shows that participants receiving ordinal feedback had a significantly higher devMean compared to those receiving continuous feedback (t = 2.523).
- The two-way and three-way interaction terms (conditVaried:catOrderrev, conditVaried:fbordinal, catOrderrev:fbordinal, and conditVaried:catOrderrev:fbordinal) were not significant, indicating that the effects of training variability, order manipulation, and feedback type did not significantly interact with each other.

@@

```{r}
model_vb <- lmer(devMean ~ condit * catOrder * fb * vb + (1|id), data = dtestAgg)
summary(model_vb)
```

Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * catOrder * fb * vb + (1 | id)
   Data: dtestAgg

@@

Fixed effects:
                                               Estimate Std. Error t value
(Intercept)                                      252.99      21.14  11.970
conditVaried                                     134.26      30.28   4.434
catOrderrev                                      -60.79      33.55  -1.812
fbordinal                                        143.77      33.87   4.244
vb350-550                                        -61.41      24.73  -2.483
vb600-800                                       -102.59      24.73  -4.148
vb800-1000                                       -66.11      24.91  -2.654
vb1000-1200                                      -22.19      25.61  -0.866
vb1200-1400                                       23.54      26.07   0.903
conditVaried:catOrderrev                        -173.94      47.39  -3.670
conditVaried:fbordinal                          -147.69      50.34  -2.934
catOrderrev:fbordinal                             70.51      49.32   1.430
conditVaried:vb350-550                           -36.84      35.43  -1.040
conditVaried:vb600-800                           -48.49      35.43  -1.369
conditVaried:vb800-1000                          -98.39      35.70  -2.756
conditVaried:vb1000-1200                        -159.64      36.33  -4.394
conditVaried:vb1200-1400                        -160.75      36.81  -4.367
catOrderrev:vb350-550                             64.52      39.37   1.639
catOrderrev:vb600-800                             97.13      39.37   2.467
catOrderrev:vb800-1000                            75.46      39.24   1.923
catOrderrev:vb1000-1200                           68.47      39.68   1.725
catOrderrev:vb1200-1400                           97.34      39.98   2.435
fbordinal:vb350-550                              -59.00      39.63  -1.489
fbordinal:vb600-800                             -120.60      39.63  -3.043
fbordinal:vb800-1000                            -104.78      40.35  -2.597
fbordinal:vb1000-1200                           -121.77      41.28  -2.950
fbordinal:vb1200-1400                           -133.56      41.92  -3.186
conditVaried:catOrderrev:fbordinal               -53.01      72.62  -0.730
conditVaried:catOrderrev:vb350-550                19.29      55.53   0.347
conditVaried:catOrderrev:vb600-800                60.66      55.61   1.091
conditVaried:catOrderrev:vb800-1000              198.56      55.52   3.576
conditVaried:catOrderrev:vb1000-1200             267.80      55.93   4.788
conditVaried:catOrderrev:vb1200-1400             249.68      56.24   4.439
conditVaried:fbordinal:vb350-550                  61.93      58.90   1.051
conditVaried:fbordinal:vb600-800                 103.53      58.90   1.758
conditVaried:fbordinal:vb800-1000                 84.75      59.47   1.425
conditVaried:fbordinal:vb1000-1200               141.77      60.19   2.356
conditVaried:fbordinal:vb1200-1400               165.62      60.88   2.721
catOrderrev:fbordinal:vb350-550                 -100.28      57.85  -1.733
catOrderrev:fbordinal:vb600-800                 -124.71      57.78  -2.158
catOrderrev:fbordinal:vb800-1000                -102.80      58.10  -1.769
catOrderrev:fbordinal:vb1000-1200                -82.52      58.75  -1.404
catOrderrev:fbordinal:vb1200-1400                -68.74      59.21  -1.161
conditVaried:catOrderrev:fbordinal:vb350-550      93.93      85.00   1.105
conditVaried:catOrderrev:fbordinal:vb600-800     133.48      85.09   1.569
conditVaried:catOrderrev:fbordinal:vb800-1000     69.46      85.23   0.815
conditVaried:catOrderrev:fbordinal:vb1000-1200   -12.91      85.74  -0.151
conditVaried:catOrderrev:fbordinal:vb1200-1400   -15.49      86.22  -0.180

@@

- The intercept (252.99) represents the estimated mean devMean for the reference group (constant training, 'orig' order, continuous feedback, and the lowest velocity band).
- conditVaried (134.26) indicates that, on average, participants in the varied training group had a higher devMean compared to the constant training group, with a significant effect (t = 4.434).
- catOrderrev (-60.79) suggests that the 'rev' order manipulation had a small and marginally significant effect on devMean (t = -1.812).
- fbordinal (143.77) shows that participants receiving ordinal feedback had a significantly higher devMean compared to those receiving continuous feedback (t = 4.244).

@@

- conditVaried:catOrderrev (-173.94, t = -3.670): The interaction between training variability and order manipulation has a significant effect on devMean.
- conditVaried:fbordinal (-147.69, t = -2.934): The interaction between training variability and feedback type has a significant effect on devMean.
- conditVaried:vb800-1000 (-98.39, t = -2.756), conditVaried:vb1000-1200 (-159.64, t = -4.394), and conditVaried:vb1200-1400 (-160.75, t = -4.367): The interaction between training variability and specific velocity bands has a significant effect on devMean.

@@

interaction_plot_1 <- ggplot(dtestAgg, aes(x = catOrder, y = devMean, color = condit)) +
  stat_summary(fun = mean, geom = "point", size = 3) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  theme_minimal() +
  labs(title = "Interaction between Training Variability and Order Manipulation",
       x = "Order Manipulation",
       y = "Mean Deviation",
       color = "Training Variability")

@@

table_2 <- dtestAgg %>%
  group_by(condit, catOrder) %>%
  summarise(mean_deviation = mean(devMean), .groups = "drop")

@@

A linear mixed model was fitted to the data with devMean as the dependent variable and condit (training variability), catOrder (order manipulation), and fb (feedback type) as fixed effects, and id (participant) as a random effect. The analysis revealed significant main effects of training variability, F(1, 2695) = 7.21, p < .01, and feedback type, F(1, 2695) = 6.36, p < .05, on devMean. Participants in the varied training group (M = 266.04, SE = 19.97) had a higher devMean compared to the constant training group (M = 212.43, SE = 13.97), indicating better performance. Participants receiving ordinal feedback (M = 269.04, SE = 22.44) also had a higher devMean compared to those receiving continuous feedback (M = 212.43, SE = 13.97). The main effect of order manipulation was not significant, F(1, 2695) = 0.19, p = .66.

The two-way and three-way interaction terms (conditVaried:catOrderrev, conditVaried:fbordinal, catOrderrev:fbordinal, and conditVaried:catOrderrev:fbordinal) were not significant, indicating that the effects of training variability, order manipulation, and feedback type did not significantly interact with each other.

To further investigate the influence of velocity bands on performance, an additional linear mixed model was fitted with devMean as the dependent variable and condit, catOrder, fb, and vb (velocity band) as fixed effects, and id as a random effect. The main effects of the velocity bands were significant, with some bands leading to significantly lower devMean values compared to the reference band (e.g., vb600-800: -102.59, t = -4.148). Moreover, significant interactions were found between training variability and order manipulation, F(1, 2689) = 13.47, p < .001, training variability and feedback type, F(1, 2689) = 8.61, p < .01, and training variability and specific velocity bands (e.g., conditVaried:vb800-1000, F(1, 2689) = 7.59, p < .01).

>>>>

```{r}
pacman::p_load(tidyverse,data.table,lme4,emmeans,here,knitr,kableExtra)
d <- readRDS(here("data/dPrune-07-27-23.rds"))

@@

dtestAgg <- dtest %>% group_by(id,condit,bandOrder,fb,vb,band,lowBound,highBound,bandInt) %>% mutate(vxCapped=ifelse(vx>1600,1600,vx)) %>%
  summarise(vxMean=mean(vx),devMean=mean(dist),vxMed=median(vx),devMed=median(dist),
            vxMeanCap=mean(vxCapped),.groups = "keep")
```

```{r}
model <- lmer(devMean ~ condit * bandOrder * fb + (1|id), data = dtestAgg)
summary(model)
```

Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * bandOrder * fb + (1 | id)
   Data: dtestAgg

@@

Fixed effects:
                                   Estimate Std. Error t value
(Intercept)                         212.430     13.967  15.209
conditVaried                         53.614     19.965   2.685
bandOrderrev                           9.478     21.811   0.435
fbordinal                            56.609     22.441   2.523
conditVaried:bandOrderrev            -45.098     30.951  -1.457
conditVaried:fbordinal              -58.510     33.172  -1.764
bandOrderrev:fbordinal               -12.767     32.312  -0.395
conditVaried:bandOrderrev:fbordinal   -3.604     47.473  -0.076

@@

- The intercept (212.430) represents the estimated mean devMean for the reference group (constant training, 'orig' order, and continuous feedback).
- conditVaried (53.614) indicates that, on average, participants in the varied training group had a higher devMean compared to the constant training group, with a significant effect (t = 2.685).
- bandOrderrev (9.478) suggests that the 'rev' order manipulation had a small and non-significant effect on devMean (t = 0.435).
- fbordinal (56.609) shows that participants receiving ordinal feedback had a significantly higher devMean compared to those receiving continuous feedback (t = 2.523).
- The two-way and three-way interaction terms (conditVaried:bandOrderrev, conditVaried:fbordinal, bandOrderrev:fbordinal, and conditVaried:bandOrderrev:fbordinal) were not significant, indicating that the effects of training variability, order manipulation, and feedback type did not significantly interact with each other.

@@

```{r}
model_vb <- lmer(devMean ~ condit * bandOrder * fb * vb + (1|id), data = dtestAgg)
summary(model_vb)
```

Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * bandOrder * fb * vb + (1 | id)
   Data: dtestAgg

@@

Fixed effects:
                                               Estimate Std. Error t value
(Intercept)                                      252.99      21.14  11.970
conditVaried                                     134.26      30.28   4.434
bandOrderrev                                      -60.79      33.55  -1.812
fbordinal                                        143.77      33.87   4.244
vb350-550                                        -61.41      24.73  -2.483
vb600-800                                       -102.59      24.73  -4.148
vb800-1000                                       -66.11      24.91  -2.654
vb1000-1200                                      -22.19      25.61  -0.866
vb1200-1400                                       23.54      26.07   0.903
conditVaried:bandOrderrev                        -173.94      47.39  -3.670
conditVaried:fbordinal                          -147.69      50.34  -2.934
bandOrderrev:fbordinal                             70.51      49.32   1.430
conditVaried:vb350-550                           -36.84      35.43  -1.040
conditVaried:vb600-800                           -48.49      35.43  -1.369
conditVaried:vb800-1000                          -98.39      35.70  -2.756
conditVaried:vb1000-1200                        -159.64      36.33  -4.394
conditVaried:vb1200-1400                        -160.75      36.81  -4.367
bandOrderrev:vb350-550                             64.52      39.37   1.639
bandOrderrev:vb600-800                             97.13      39.37   2.467
bandOrderrev:vb800-1000                            75.46      39.24   1.923
bandOrderrev:vb1000-1200                           68.47      39.68   1.725
bandOrderrev:vb1200-1400                           97.34      39.98   2.435
fbordinal:vb350-550                              -59.00      39.63  -1.489
fbordinal:vb600-800                             -120.60      39.63  -3.043
fbordinal:vb800-1000                            -104.78      40.35  -2.597
fbordinal:vb1000-1200                           -121.77      41.28  -2.950
fbordinal:vb1200-1400                           -133.56      41.92  -3.186
conditVaried:bandOrderrev:fbordinal               -53.01      72.62  -0.730
conditVaried:bandOrderrev:vb350-550                19.29      55.53   0.347
conditVaried:bandOrderrev:vb600-800                60.66      55.61   1.091
conditVaried:bandOrderrev:vb800-1000              198.56      55.52   3.576
conditVaried:bandOrderrev:vb1000-1200             267.80      55.93   4.788
conditVaried:bandOrderrev:vb1200-1400             249.68      56.24   4.439
conditVaried:fbordinal:vb350-550                  61.93      58.90   1.051
conditVaried:fbordinal:vb600-800                 103.53      58.90   1.758
conditVaried:fbordinal:vb800-1000                 84.75      59.47   1.425
conditVaried:fbordinal:vb1000-1200               141.77      60.19   2.356
conditVaried:fbordinal:vb1200-1400               165.62      60.88   2.721
bandOrderrev:fbordinal:vb350-550                 -100.28      57.85  -1.733
bandOrderrev:fbordinal:vb600-800                 -124.71      57.78  -2.158
bandOrderrev:fbordinal:vb800-1000                -102.80      58.10  -1.769
bandOrderrev:fbordinal:vb1000-1200                -82.52      58.75  -1.404
bandOrderrev:fbordinal:vb1200-1400                -68.74      59.21  -1.161
conditVaried:bandOrderrev:fbordinal:vb350-550      93.93      85.00   1.105
conditVaried:bandOrderrev:fbordinal:vb600-800     133.48      85.09   1.569
conditVaried:bandOrderrev:fbordinal:vb800-1000     69.46      85.23   0.815
conditVaried:bandOrderrev:fbordinal:vb1000-1200   -12.91      85.74  -0.151
conditVaried:bandOrderrev:fbordinal:vb1200-1400   -15.49      86.22  -0.180

@@

- The intercept (252.99) represents the estimated mean devMean for the reference group (constant training, 'orig' order, continuous feedback, and the lowest velocity band).
- conditVaried (134.26) indicates that, on average, participants in the varied training group had a higher devMean compared to the constant training group, with a significant effect (t = 4.434).
- bandOrderrev (-60.79) suggests that the 'rev' order manipulation had a small and marginally significant effect on devMean (t = -1.812).
- fbordinal (143.77) shows that participants receiving ordinal feedback had a significantly higher devMean compared to those receiving continuous feedback (t = 4.244).

@@

- conditVaried:bandOrderrev (-173.94, t = -3.670): The interaction between training variability and order manipulation has a significant effect on devMean.
- conditVaried:fbordinal (-147.69, t = -2.934): The interaction between training variability and feedback type has a significant effect on devMean.
- conditVaried:vb800-1000 (-98.39, t = -2.756), conditVaried:vb1000-1200 (-159.64, t = -4.394), and conditVaried:vb1200-1400 (-160.75, t = -4.367): The interaction between training variability and specific velocity bands has a significant effect on devMean.

@@

interaction_plot_1 <- ggplot(dtestAgg, aes(x = bandOrder, y = devMean, color = condit)) +
  stat_summary(fun = mean, geom = "point", size = 3) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  theme_minimal() +
  labs(title = "Interaction between Training Variability and Order Manipulation",
       x = "Order Manipulation",
       y = "Mean Deviation",
       color = "Training Variability")

@@

table_2 <- dtestAgg %>%
  group_by(condit, bandOrder) %>%
  summarise(mean_deviation = mean(devMean), .groups = "drop")

@@

A linear mixed model was fitted to the data with devMean as the dependent variable and condit (training variability), bandOrder (order manipulation), and fb (feedback type) as fixed effects, and id (participant) as a random effect. The analysis revealed significant main effects of training variability, F(1, 2695) = 7.21, p < .01, and feedback type, F(1, 2695) = 6.36, p < .05, on devMean. Participants in the varied training group (M = 266.04, SE = 19.97) had a higher devMean compared to the constant training group (M = 212.43, SE = 13.97), indicating better performance. Participants receiving ordinal feedback (M = 269.04, SE = 22.44) also had a higher devMean compared to those receiving continuous feedback (M = 212.43, SE = 13.97). The main effect of order manipulation was not significant, F(1, 2695) = 0.19, p = .66.

The two-way and three-way interaction terms (conditVaried:bandOrderrev, conditVaried:fbordinal, bandOrderrev:fbordinal, and conditVaried:bandOrderrev:fbordinal) were not significant, indicating that the effects of training variability, order manipulation, and feedback type did not significantly interact with each other.

To further investigate the influence of velocity bands on performance, an additional linear mixed model was fitted with devMean as the dependent variable and condit, bandOrder, fb, and vb (velocity band) as fixed effects, and id as a random effect. The main effects of the velocity bands were significant, with some bands leading to significantly lower devMean values compared to the reference band (e.g., vb600-800: -102.59, t = -4.148). Moreover, significant interactions were found between training variability and order manipulation, F(1, 2689) = 13.47, p < .001, training variability and feedback type, F(1, 2689) = 8.61, p < .01, and training variability and specific velocity bands (e.g., conditVaried:vb800-1000, F(1, 2689) = 7.59, p < .01).
